Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic Models for Estimation of Distribution Genetic Programming

### 2023-01-18 slides.Rmd
Wed Jan 18 16:00:14 CET 2023: update-remote.sh

```{bash recompile_results, eval=FALSE, include=FALSE}

@@

# 2nd generation Pre-Training
/Users/rmn/miniconda3/envs/dataScience/bin/python /Users/rmn/masterThesis/eda-gp-2020/experiments/2ndGenPT_airfoil_2hl_150hn_fullRun/re_evaluate_2ndGenPT_airfoil_2hl_150hn_fullRun.sh

@@

## DAE-GP - Entwicklung DAE-LSTM Dimension

@@

>>>>

```{bash recompile_results, echo=TRUE, eval=FALSE, include=FALSE}

@@

# 2nd generation Pre-Training
bash /Users/rmn/masterThesis/eda-gp-2020/experiments/2ndGenPT_airfoil_2hl_150hn_fullRun/re_evaluate_2ndGenPT_airfoil_2hl_150hn_fullRun.sh

echo Done recompiling Results, Plots, Diagrams, etc!

@@

<!--
## DAE-GP - Entwicklung DAE-LSTM Dimension

@@

--->
